Data Prep

### 2025-02-04 scripts/00.0_dataPrep.qmd
tidying up

```{r load-packages}
library(vultureUtils)
library(sf)
library(tidyverse)
library(move)
library(feather)
library(readxl)
library(elevatr)
library(here)
library(furrr)
future::plan(future::multisession, workers = 5) # this will last for the whole R session.

@@

```{r}
capture_sites <- read.csv(here("data/raw/capture_sites.csv"))
carmel <- read.csv(here("data/raw/all_captures_carmel_2010-2021.csv"))
removed_captures <- removeCaptures(data = cleaned, 
                                       captureSites = capture_sites, 
                                       AllCarmelDates = carmel, 
                                       distance = 500, idCol = "Nili_id")

@@

mutate(age = year - birth_year, #XXX consider moving this up to the age/sex section. Why is it happening here?
         sex = case_when(sex == "f/m" ~ "u",
                         TRUE ~ sex)) %>%

@@

```{r region-masking}
mask <- sf::st_read(here("data/raw/CutOffRegion.kml"))

>>>>

```{r load-packages}
# First install the package from GitHub (do this in the console, not the script)
# remotes::install_github("kaijagahm/vultureUtils")
# devtools::install_github("kaijagahm/vultureUtils")
library(vultureUtils)
library(sf)
library(tidyverse)
library(move) # the R package that allows you to download Movebank data through R instead of manually
library(feather)
library(readxl)
library(elevatr)
library(here)
library(furrr)
future::plan(future::multisession, workers = 5) # this will last for the whole R session.

@@

```{r}
capture_sites <- read.csv(here("data/raw/capture_sites.csv"))
carmel <- read.csv(here("data/raw/all_captures_carmel_2010-2021.csv"))
removed_captures <- vultureUtils::removeCaptures(data = cleaned, 
                                       captureSites = capture_sites, 
                                       AllCarmelDates = carmel, 
                                       distance = 500, idCol = "Nili_id")

@@

@@

```{r region-masking}
mask <- sf::st_read(here("data/CutOffRegion.kml"))
